---
title: RMarkdown Primer
author: Xiekang Zhang
output: 
    html_document:
        number_sections: true
        toc: true
        toc_float:
            collapsed: false
            smooth_scroll: true
        code_download: true
        df_print: "paged"
    pdf_document: 
        number_sections: true
        toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE, fig.align = 'center')
```


# Level 1 Heading

This a sentence. Any text here gets rendered as normal text.

A blank line creates a new paragraph, still in the same section.

# Another Level 1 Heading

More text.

## Level 2 Heading

This is a subsection under the level 1 heading.

# Back to Level 1

This starts a new section.

# Text Formatting

_italic_

__bold__

___italic and bold___

# Lists {#TheLists}

## Unordered Lists

- apples
- bananas
- oranges
- kiwis

## Ordered Lists

### Numbered Lists

1. New York
1. New Jersey
1. Naples
1. Connecticut
1. Detroit

### Lettered Lists

a. Coal
a. Wood
a. Gas

## Nested Lists

1. New York
    a. Coal
    a. Wood
    a. Gas
        - Baker's Pride
        - Bari
    a. Electric
1. New Jersey
1. Philadelphia
1. Detroit

# Links

[Google](www.google.com)

[Check out the pizza section](#TheLists)

# Math

$$
    \bar{x} = \sum_{i=1}^n \frac{x_i}{n}
$$

Inline equations look like $y = mx + b$. 

# Footnotes

We^[Everyone enjoying this video] are learning markdown^[Markdown is a simple way of writing documents] on our way to learning RMarkdown. 

# Simple Code

```{r this-label}
1 + 1
```

```{r multiplication}
4 * 2
```

```{r subtraction}
5 - 3
```

```{r multi-line}
1 + 1
4 * 2
5 - 3
```

# Data Display
```{r show-data}
#install.packages("ggplot2")
#require('ggplot2')
data(diamonds, package='ggplot2')
head(diamonds)
```

```{r show-data-2}
knitr::kable(head(diamonds))
```

```{r show-data-3}
#install.packages("DT")
DT::datatable(head(diamonds))
```

```{r show-data-4}
head(diamonds)
```

# Plots
```{r simple-plot}
plot(1:10)
```

```{r another-plot, fig.cap='A simple plot', cache=TRUE, echo=FALSE}
plot(1:10)
```

