---
title: "Slideshow Fun"
author: "Xiekang"
date: '2022-06-22'
output: 
    ioslides_presentation:
        logo: logo.png
        widescreen: yes
        self_contained: yes
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Fruit - Level 2 for a new slides

- Apples
- Bananas
- Kiwis

<div class="notes">
- This is a note to the speaker
- The audience won't see it
</div>

## Graph Slide

```{r load-date}
library(ggplot2)
data(diamonds)
```
```{r hist, message=FALSE, fig.align='center'}
possible <- names(diamonds)[sapply(diamonds, is.numeric)]

selectInput(
  inputId="SelCol",
  label="Choose a column",
  choices=possible
)

renderPlot(
  ggplot(diamonds, aes_string(x=input$SelCol)) + geom_histogram()
)
```

<div class="notes">
Histogram of diamond prices
</div>